---
title: "Project protocol"
subtitle: "Registered reports funding models: a qualitative feasibility study"
author: "Christopher Chambers, Katie Drax,  Marcus Munaf&ograve; and Jacqueline Thompson"
date: "November 2019"
output: pdf_document
csl: apa.csl
bibliography: rr_library.bib
---

```{r setup, include=F} 
knitr::opts_chunk$set(echo = F)

library(pander)
library(dplyr)
library(readr)

df <- read.csv("../mini_review/analysis/analysis_clean.csv", stringsAsFactors = F)


```


# Background

## Registered reports

Registered reports (RRs) are a research report format where submissions undergo a two-stage peer-review process, once before data collection when a protocol containing the Introduction and Methods sections are reviewed and once after, when the complete manuscript is reviewed and adherence to the stage one submission is checked. 
Protocols that pass stage one are granted in-principle acceptance (IPA) meaning they cannot be rejected based on any outcomes observed in the stage two.
These two components, pre-study review and IPA are what define an RR. To date, 206 journals offer RRs (https://cos.io/rr/). Detailed discussion of the potential benefits and limitations of RRs can be found in several articles including @grand2018, @vantveer2016, @parker2019, @chambers2014 and @marsden2018a. 
These non-empirical articles lay out the theoretical impacts that logically follow from offering or authoring RRs. 
For example that peer-review before data collection could improve study designs or that IPA reduces publication bias for certain results. 
The acceptability of RRs is also clear from the speed of uptake by journals. 
However there is minimial empirical evidence that these theoretical impacts are realised in practice. 

Like any intervention the success of RRs will be partly dependent on the quality of their implementation. @hardwicke2018  surveyed 145 stage one and stage two RRs, of which 43% had not shared their IPA, privately or publicly, and only 24% of these gave a reason why. 
Shared protocols were done so sub-optimally. 
[insert].
Another issue is terminology. Of the 54 completed and published RRs half were clearly labelled as an RR. 
Similar to the confusion between 'registration' and 'pre-registration' @rice2019 a qualitative survey indicates editorial board members can be confused about what RRs are (@woznyj2018)[check].


```{r, echo=F, include = F}

osf <- read.csv(url("https://osf.io/n5czt//?action=download"))

freq <- function(col){
  prop.table(table(col))
}

freq(osf$protocolMadeAvailable)
freq(osf$reasonForNoShare)

sum(is.na(osf$identifiesAsRR))
freq(osf$identifiesAsRR)

#registered: method by which the IPA protocol was registered. "yes" means the protocol was formally registered. "OSF timestamp" means the protocol was available on the Open Science Framework (OSF) but was not formally registered.  "published" means the IPA protocol was published as an article in the journal. "no" means the IPA protocol has no registration features, it is simply available on the Internet.

freq(osf$registered)
```

As the number of RR journals increases it become more important to understand how to ensure the quality of their implementation at a large scale. 
Among other things this will allow precise evaluations of impact of RRs as a whole, otheriwse large variation in implementation will make evlauations noisy or ungeneralisable. 

## Funder-RR journal partnerships

Despite the lack of evidence for RRs efficacy research funders are extending the new format. 
Six funders are currently in 'partnerships' with RR journals. Though none of the funder-RR partnerships are identical they all involve one funder and one RR journal collaborating to streamline the transition from funding application to journal publication. The six existing partnerships are listed below:

* The Flu Lab, PLOS, and the Center for Open Science (https://cos.io/our-services/research/flulab/)
* Cancer Research UK and Nicotine & Tobacco Research journal (@munafo2017)
* Global Research Awards for Nicotine Dependence and Nicotine & Tobacco Research journal (http://www.grandawardsprogram.org/news/news-and-announcements.html)
* Children's Tumor Foundation and PLOS ONE (https://blogs.plos.org/everyone/2017/09/26/registered-reports-with-ctf/)
* The Association for Politics & The Life Sciences and Politics and the Life Sciences journal (https://www.cambridge.org/core/journals/politics-and-the-life-sciences/information/call-for-papers-psychophysiology-cognition-and-political-differences)
* Prostate Cancer Foundation - Movember Foundation Reproducibility Initiative and PeerJ journal (https://osf.io/ih9qt/wiki/home/)
* Language Learning Early Career Research Grant Program and Language Learning journal (https://onlinelibrary.wiley.com/page/journal/14679922/homepage/grant_programs.htm)

Previously the Center for Open Science funded RRs of replication studies submitted to Perspectives on Psychological Science journal (https://www.psychologicalscience.org/observer/aps-replication-initiative-underway) but the partnership has now finished.

Early proposals of funder-RR partnerships from @marcus2017a and the Center for Open Science (https://web.archive.org/web/20170202152633/https://cos.io/rr/), suggested that authors submit a detailed procotol before the research is funded. 
The protocol is then simultaneously reviewed by a funder and a journal. 
Successful submissions receive funding from the funder and IPA  from the journal, potentially on the same day. 
Another option is a staggered review process whereby a funder receives a conventional grant application and successful applications are invited to submit a stage one protocol to the partnering journal, or possibly journals. 
None of the six partnerhips exactly follow exactly the staggered or simultaneous review processes described here. 
However they are all closer to the staggered review than the simultaneous review. 
See [Appendix A](## Appendix A. Funder-RR partnerships and their timelines) for a detailed description of the six partnerships' timelines and processes.

# Rationale for study

The number of journals offering RRs is rapidly increasing and six funder-RR journal partnerships already exist.
This uptake demonstrates that many journals and several funders believe the potential benefits of RRs outweight their potential risks but the truth of these beliefs remains to be determined. 
A randomised control trial (RCT) would provide the strongest evidence for the impacts of RRs or partnerships.
However given that no such RCT exists it is difficult to know how either RCT should be designed.
Feasibility or pilot studies would help inform a RCT to ensure the validty and reliability of its results.
Here we use [cite] definition of feasibility and pilot studies.
[give definition]

A RCT of RRs is likely to be more immediately feasible than a RCT of partnerships since there are far more RR journals. 
However, we are planning to conduct an RCT of the impacts of partnerships rather than RRs because [?] we believe we have access to funder personnel that other researchers may not. 
MM is the editor of Nicotine and Tobacco Research and CC is on the Center for Open Science steering committee for RRs [check]. 
Additionally a RCT of partnerships may also assess the impacts of RRs since the RR process is nested within a partnership. 

We will conduct a qualitative feasibility study to inform a pilot RCT to assess the impacts of partnerships.
Currently we do not know how acceptable partnerships are to their stakeholders nor how a RCT of their impacts should be designed and conducted.
These unknowns means a feasibility study is required to inform a future pilot.
we have chosen a qualitative design because funder-RR partnerships are rare and have heterogeneous processes. 
The provider's and user's experience of partnerhips is likely to be highly variable and it will be difficult  to yield a large enough sample for inferential statistics. 

# Study objectives and research questions

The aim of our study is to determine the feasibility of conducting a RCT to answer the question: 'do RR partnerships (i.e. of funders & journals working together to offer authors RRs) benefit funders?'.

To achieve this aim our study will investigate the following research questions: 

1. What partnership model is the most feasible and beneficial?
2. What outcome measures are valid, reliable, feasible and yield high responsiveness?

related to design and delivery of the intervention and future RCT:

1. What are the characteristics of existing partnerships models?
1. What partnership model offers the most benefit to all stakeholders (editors, reviewers, funders, authors, researchers)?
1. What partnership model is the most acceptable to all users (editors, reviewers funders and authors)?
1. How might implementation of a partnership model vary?
1. How could participants be recruited?
1. What positive effects might stakeholders experience?
1. If any, What is responsible for these positive effect?
1. What unintended effects might stakeholders experience?
1. If any, what is responsible fo rthese unintended effects?
1. What outcomes that indicate benefit to all stakeholders (editors, reviewers, funders, authors, researchers) can be collected?

# Methods

This protocol is reported in line with the COREQ checklist [Appendix B](#Appendix B. Completed COREQ checklist)

## Design

Semi-structured interviews were chosen over other interview formats to ensure essential questions are answered to allow comparison across participants but allow follow-up questions to be asked if important topics emerge. 
They are also preferable to focus groups because focus groups are typically more time-consuming to transcribe and will be difficult to organise for a target population that is small and geographically dispersed.

2. What is the experience of stakeholders in existing partnerships? This will include their views on their model's:

* potential improvements
* feasibility of improvements
* strengths
* weaknesses 
* suitability for different research types
* suitability for different funders
* impact on research quality 
* impact on manuscript quality
* well-being
* efficiency of research process (i.e. from idea conception to publication)
* impact on funders reputation
* impact on researcher's career prospects

## Respondents and recruitment

To understand the experiences of all stakeholder groups in funder-RR partnerships we will need to recruit [number?] people from each of the four stakeholder groups, (1) authors of partnership submissions, (2) personnel at partner funders (e.g. reviewers), (3) personnel at partner journals (e.g. reviewers and editors) and (4) readers of partnership publications. 

People will be sampled [how?]. 

### Inclusion criteria

[why participant were most appropriate to provide knowledge]

### Sample size determination

We expect this sample size (up to N = [sample?]) to be [justification? feasibility? data saturation?]. 

## Measures

## Materials

## Transcription

We are only interested in the information communicated during the interview, not how it is communicated. 
Therefore interviews will be trascribed by RC using denaturalised transcription (@oliver2005).
This means utterances or noises deemed unnecessary for understanding the original meaning of the content will not be transcribed.
RC will use the transcription notation described in [Table 1](### *Table 1. Transcription notation*)
See [Table 1](Table 1) for the transcription protocol for this study.

### *Table 1. Transcription notation*

```{r}

# df of audio elements that won't be transcribed

no <- data.frame(
  Audio = c("Emotional content (e.g. laughter, sighing, crying, emphasis, coughing, exhalation, inhalation, sneezing, sniffing)", "Prosodic features (e.g. pitch, loudness)", "Incomplete/interrupted speech", "Duration of pauses", "Filler words", "Background noises", "Overlapping speech", "Unintelligable speech", "Uncertain speech"),
  Notation = rep("Not transcribed or noted"),
  stringsAsFactors = F
)

# df of audio elements that will be transcribed and their notation

yes <- data.frame(
  Audio = c("Pauses", 
        "Questions (e.g. direct questions or upward inflection)", 
        "Exclamations", 
        "Mispronunciations, informal contractors or slang",
        "Quotations",
        "Irrelevant information (e.g. welcomes, goodbyes, small talk)",
        "Names"),
  Notation = c("Comma ',' or full-stop '.'",
        "Question mark '?'", 
        "Exclamation mark '!'", 
        "Transcribed as correct spelling if possible. Transcribed as respondent says them if not.",
        "Write without quotation marks (e.g. he said I could)", 
        "Not transcribed. Provide a summary in square brackets (e.g. [Interviewer welcomes respondent and ask about each other's wellbeing]",
        "Not transcribed on respondents request. Provide a general term describing the removed names (e.g. [person's name], [workplace]"),
  stringsAsFactors = F
)

# bind dfs of audio elements that will (yes) and won't (no) be transcripted & present as a table

rbind(no, yes) %>%
  arrange(Audio)%>%
  pander(split.cell = 80, split.table = Inf, justify = "left")

```


## Procedure

KD and JT will then invite selected people by email [or phone?].
If an individual agrees to particpate the information sheet and online consent form will be emailed to them. 
Once consent is received the respondent and interviewer will arrange the interview for a mutally convenient time.
Interviews will be face-to-face in Bristol or by telephone, which ever the respondent prefers. However travel will not be reimbused.
If multiple respondents reside in the same place and can be interviewed on the same day it may be justifiable for the interviewer to offer to travel to meet them.
JT or KD will conduct the interviews, they will be audio recorded and last around [45?] minutes.
If the audio recording is of poor quality the respondent will be invited for a second interview.
RC will transcribe the interviews.


## Analysis plan

### Thematic analysis

[highlighting, examining & recording patterns in data (coding)]

### Data saturation

[assessing & reporting]


# Ethical Considerations and Informed Consent

Ethics approval has been/will be obtained from the School of Psychological Science Research Ethics Committee  at the University of Bristol (Approval Code: [insert once given] ).  
The study will be conducted according to the revised Declaration of Helsinki  (2013) and the 1996 ICH Guidelines for Good Clinical Practice E6(R1). 
The investigator will explain the nature, purpose and risks of the study to the participant. 
The interviewee will receive the information sheet in advance of the study session. There will be no time restriction on how long interviewees take to respond. 
Therefore, interviewees will be given sufficient time to read the information, consider any implications, and raise any questions with the investigators prior to making a decision to participate. 
At the start of the study session interviewees will be given the opportunity to read the information sheet again and ask the investigator questions. 
Written consent will then be obtained. Interviewees will be informed that they are free to withdraw at any time.

# Safety
 
There are no expected hazards, due to the study consisting of an interview of non-vulnerable people that includes no personal or sensitive questions.

# Data Management

All aspects of the Data Protection Act will be adhered to. Consent forms will be retained by the School of Psychological Science for a period of 10 years after study completion. 
All project materials (including the data, analysis code, protocols, interview schedules) will be hosted on the OSF. Almost everything will be hosted publicly, except the audio recordings which will remain private [?]. 

## Anonymised project data

[EDIT: Case report forms (CRFs) and electronic data will be anonymised by a unique numeric identifier. CRFs will be stored in a locked office. All data requested on the CRF will be recorded. All missing data will be explained. If any entry errors are made, a single straight line will be drawn through the incorrect entry and the correct data entered above it; to correct such an error. All such changes will be initialed and dated. Once data from CRFs have been inputted into a data spreadsheet they will undergo a reliability check (20% check by independent researcher). If an error rate greater than 1% is obtained the data will be re-inputted in full and assessed again. After the data have been positively assessed, the CRFs will be destroyed in the School's confidential waste facility .

Original computer data files will be backed up on a secured University of Bristol network drive. At the end of the study, electronic study data (including finalised data sheet) will be transferred to a designated University of Bristol Research Data Storage Facility for long-term archiving. Study data will be kept for a minimum of 15  years. At the appropriate time the data sheet will be locked and made open using the University of Bristol Research Data Repository .]

[See Table 1 - how can we anonymise text? There are several text anonymisation tools available]

## Participant contact details

Respondent contact details and respondent identifier logs will be stored on password protected university computers and kept confidential. These will be kept for one year after study completion or until data are made open (whichever comes first), after which these documents will be destroyed

## Revoked data

If a participant decides that they do not want their data used after their participation they have the right to request that the data are withdrawn. They can request this up to one year after study completion or until the data are made open (whichever comes first).

# Quality Control and Quality Assurance
 
[EDIT: The investigators will be responsible for data quality. 
After approximately 10% of data collection has been completed, the study will undergo an in-house quality assessment.
During this monitoring process all CRFs and study documents will be assessed as well as the investigators laboratory management and participant engagement, and corrected where necessary.

Post-study checks will be conducted on data entry by an independent researcher. This researcher will re-enter 20% of hardcopy participant data. A threshold of 1% will be used, whereby error rates greater than 1% will require the data to be re-entered. A 100% check will be made on allocation to test condition.]

This protocol was completed using the COREQ 

# Insurance

This study will be sponsored by the University of Bristol. 
The University has Public Liability Insurance to cover the liability of the University to research participants. In the event that something goes wrong and a participant is harmed during the research study there are no special compensation arrangements. 
If a participant is harmed and this is due to someone's negligence then they may have grounds for a legal action for compensation against Bristol University or one of the other parties to the research, but they may have to pay their own legal costs.

# Publication Policy
 
The findings from this research study may be published in an appropriate scientific journal (and made available open access), and/or presented at an appropriate meeting. 
Study data will be collected and held by the study investigators. The data will be made available for sharing via a University of Bristol online data repository.

# Project personnel

Katie Drax,
School of Psychological Science ,
12a Priory Road,
Bristol, BS8 1TU,
katie.drax@bristol.ac.uk 

Marcus Munaf&ograve;,
School of Psychological Science,
12a Priory Road,
Bristol, BS8 1TU,
marcus.munafo@bristol.ac.uk 

Jacqueline Thompson,
School of Psychological Science,
12a Priory Road,
Bristol, BS8 1TU,
jackie.thompson@bristol.ac.uk 

Christopher Chambers
[insert]

# Contributions and Authorship
 
KD and JT are the guarantors of the project. MM will supervise the project. [contributions to protocol]

# Funding Source

This work is being funded by the John Climax Benevolent Fund. 
The funder will support the conduct of the work by paying KD's stipend. 
The funder has and will have no input on any aspect of the project, such the protocol design, data collection, data analysis nor interpretation or publication of results. 

[others?]

# Conflicts of Interest

[Chris & Marcus?]

# Appendices

## Appendix A. Funder-RR partnerships and their timelines

Children's Tumor Foundation (CTF) & PLoS ONE: Drug Discovery Initiative - Registered Reports (DDIRR)

- Researchers submit letter of interest (LOI; 3 pages) to CTF 
- Neurofibromatosis experts review the LOIs 
    - This is done by appointment over the phone to CTF-DDIRR director, Salvo, and transcribed-- cuts down on turnaround waiting for reviews 

- CTF decides on basis of reviews which LOIs to invite for full submission 
- Researchers make full submission in Stage 1 RR format; this is submitted to PLoS One, along with original CTF reviews, for review (including statistical review) by PLoS ONE reviewers 
- Stage 1 review suggestions sent back to authors, who are asked to incorporate and resubmit within 1-2 weeks 
- If reviewers (or editor??) are satisfied -- IPA granted [correct]
- Authors post registrations ASAP after IPA 
- Stage 1 protocols are not published following IPA. Instead they are held in reserve by the journal and integrated into the completed article following approval of the final Stage 2 manuscript. 
  

CHDI Foundation & PLoS Biology

- Science directors at CHDI (who work closely with funded teams) propose RR to research groups (SDs meet with teams at an official Joint Steering Committee every 3 months) 
- Research groups send pre-submission enquiry to PLoS 
- If successful, they write the RR and submit Stage 1 
- (project will be funded either way - part of already funded groups) 
  

Cancer Research UK (CRUK) & Nicotine and Tobacco Research (N&TR)

- CRUK evaluate possible submissions' relevance to N&TR subject areas 
- N&TR editor confirms which would be relevant to the journal 
- CRUK evaluate submissions & decide which ones to fund 
- After receiving their award letter, funded projects are given the opportunity to submit RR to N&TR 
- N&TR assesses Stage 1 and eventually Stage 2 submissions like a normal RR
        	
[insert images]

## Appendix B. Completed COREQ checklist

# References
